---
title: "UBS Analysis"
author: "Rachelle Cha"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
    theme: journal
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE,
  warning = FALSE
)
library(tidycensus)
library(tidyverse)
library(leaflet)
library(sf)
library(viridis)
library(styler)
options(tigris_use_cache = TRUE)
```

```{r}
# The website says the Amcerican Community Survey (ACS) has their most recent data set as 2014-2018. The ACS includesvariables on social, economic, housing, and demographic aspects. It has 25,070 variables.

var <- load_variables(year = 2018, dataset = "acs5")
```

```{r}
# Finding the demographic variables and renaming them in a list
demo_varsacs5 <- c(
  associates = "B15003_021",
  bachelors = "B15003_022",
  poverty = "B17001_002",
  female = "B01001_026",
  male = "B01001_002",
  diff_stateHouse = "B07013_014", 
  diff_stateRent = "B07013_015", 
  diff_countyHouse = "B07013_011", 
  diff_countyRent = "B07013_012", 
  house_val = "B25107_001",
  self_income = "B19053_002", 
  #population = "B01003_001", #*
  private_ins = "B27002_001", #* 
  health_ins = 'B27001_001',
  public_ins = "B27003_001",
  income = "B06011_001",
  male_car = "B08006_019",
  female_car = "B08006_036",
  pharm = "B24115_202"
)
```


[Census tracts](https://www.census.gov/programs-surveys/geography/about/glossary.html) are small, relatively permanent statistical subdivisions of  counties designed to be relatively homogeneous units with respect to population characteristics, economic status, and living conditions. They are updated by local participants prior to each decennial census as part of the Census Bureau's Participant Statistical Areas Program. Census tracts generally have a population size between 1,200 and 8,000 people, with an optimum size of 4,000 people. Census tract boundaries never cross county lines

```{r}
# We have to use tracts so that we can get geographical information using sf are leaflet
nj_demo_tracts <- get_acs(
  state = "NJ",
  geography = "tract",
  variables = demo_varsacs5,
  # Use 2018 as year for more recent data
  year = 2018,
  geometry = TRUE,
  keep_geo_vars = TRUE
) %>%
  # 4326 is most common map form
  st_transform(4326)
```

```{r}
# Function to create tracts
tracts_func <- function(data, county_n, var_n) {
  data %>%
    # Filters the county
    filter(COUNTYFP == county_n) %>%
    # Filters for the variable from our variable list
    filter(variable == var_n)
}
```

```{r}
#Function to pull variable from all tracts in NJ
alco_func <- function(var_n){
  nj_demo_tracts %>%
  filter(COUNTYFP == "001" 
         | COUNTYFP == "003" 
         | COUNTYFP == "005" 
         | COUNTYFP == "009" 
         | COUNTYFP == "007"
         | COUNTYFP == "011"
         | COUNTYFP == "013" 
         | COUNTYFP == "015" 
         | COUNTYFP == "017" 
         | COUNTYFP == "019"
         | COUNTYFP == "021"
         | COUNTYFP == "023"
         | COUNTYFP == "025"
         | COUNTYFP == "027"
         | COUNTYFP == "029"
         | COUNTYFP == "031"
         | COUNTYFP == "033"
         | COUNTYFP == "035"
         | COUNTYFP == "037"
         | COUNTYFP == "039"
         | COUNTYFP == "041") %>% 
  filter(variable == var_n) 
}
```

```{r}
#function to color the map. takes in string color pallette and mapping variable
pal_func <- function(color, var_name){
  colorNumeric(
  palette = color,
  domain = var_name$estimate,
  reverse = TRUE
  )
}
```

```{r}
nj_pop <- nj_demo_tracts %>% 
  filter(COUNTYFP == "001" 
         | COUNTYFP == "003" 
         | COUNTYFP == "005" 
         | COUNTYFP == "009" 
         | COUNTYFP == "007"
         | COUNTYFP == "011"
         | COUNTYFP == "013" 
         | COUNTYFP == "015" 
         | COUNTYFP == "017" 
         | COUNTYFP == "019"
         | COUNTYFP == "021"
         | COUNTYFP == "023"
         | COUNTYFP == "025"
         | COUNTYFP == "027"
         | COUNTYFP == "029"
         | COUNTYFP == "031"
         | COUNTYFP == "033"
         | COUNTYFP == "035"
         | COUNTYFP == "037"
         | COUNTYFP == "039"
         | COUNTYFP == "041") %>% 
  select(-(moe)) %>%
            spread(key = variable, value = estimate)  %>% 
  mutate(estimate = female + male)

nj_pop
```

```{r}

drop = c("associates",
  "bachelors",
  "poverty",
  "diff_stateHouse", 
  "diff_stateRent", 
  "diff_countyHouse", 
  "diff_countyRent", 
  "house_val",
  "self_income", 
  "health_ins",
  "income",
  "male_car",
  "female_car",
  "pharm",
  "female",
  "male",
  "population")
nj_pop <- nj_pop[,!(names(nj_pop) %in% drop)]
```

```{r}
car <- nj_demo_tracts %>% 
  filter(COUNTYFP == "001" 
         | COUNTYFP == "003" 
         | COUNTYFP == "005" 
         | COUNTYFP == "009" 
         | COUNTYFP == "007"
         | COUNTYFP == "011"
         | COUNTYFP == "013" 
         | COUNTYFP == "015" 
         | COUNTYFP == "017" 
         | COUNTYFP == "019"
         | COUNTYFP == "021"
         | COUNTYFP == "023"
         | COUNTYFP == "025"
         | COUNTYFP == "027"
         | COUNTYFP == "029"
         | COUNTYFP == "031"
         | COUNTYFP == "033"
         | COUNTYFP == "035"
         | COUNTYFP == "037"
         | COUNTYFP == "039"
         | COUNTYFP == "041") %>% 
  select(-(moe)) %>%
            spread(key = variable, value = estimate)  %>% 
  mutate(estimate = female_car + male_car)

car
```


```{r}
drop = c("associates",
  "bachelors",
  "poverty",
  "diff_stateHouse", 
  "diff_stateRent", 
  "diff_countyHouse", 
  "diff_countyRent", 
  "house_val",
  "self_income", 
  "health_ins",
  "income",
  "male_car",
  "female_car",
  "pharm",
  "female",
  "male",
  "population")
car <- nj_pop[,!(names(nj_pop) %in% drop)]
```


```{r}
# Function for creating leaflet map
map_func <- function(data, title, title2) {
  data %>%
    leaflet(width = "100%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(
      label = ~ str_extract(NAME.y, "^([^,]*)"),
      stroke = FALSE,
      smoothFactor = 0,
      fillOpacity = 0.7,
      color = ~ pal(estimate)
    ) %>%
    addLegend("bottomright",
      pal = pal,
      values = ~estimate,
      title = title,
      opacity = 1
    ) %>%
    addControl(title2, position = "topright")
}
```

```{r}
# Read in Museums

m <- read.csv(file = "~/Desktop/UBS/m.csv")

m <- subset(m, m$State..Administrative.Location. == "NJ" & m$State.Code..FIPS. == 34)

head(m)

```


# Poverty
## Number of People Living in Poverty ccc

```{r}
poverty_map <- alco_func("poverty")
poverty_map
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", poverty_map)

map_func(poverty_map, "Number of People (Ones)", "Poverty in New Jersey")
```

# Bachelors
## Number of People with Bachelors Degrees by Census Tract

```{r}
bachelors <- alco_func("bachelors")
bachelors
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", bachelors)

map_func(bachelors, "Number of People (Ones)", "Bachelors Degrees in New Jersey")
```

# Associates
## Number of People with Assocites Degrees by Census Tract

```{r}
associates <- alco_func("associates")
associates
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", associates)

map_func(associates, "Number of People (Ones)", "Bachelors Degrees in New Jersey")
```

# House Value
## Housing Value in New Jersey by Census Tract

```{r}
house_val <- alco_func("house_val")
house_val
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", house_val)

map_func(house_val, "House Value (Dollars)", "Housing Value in New Jersey")
```

# Population

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", nj_pop)

map_func(nj_pop, "Nubmer of People (Ones)", "Population in New Jersey")
```

# Health Insurance
## Number of People with Health Insurance (Private and Public) by Census Tract

```{r}
health_ins <- alco_func("health_ins")
health_ins
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", health_ins)

map_func(health_ins, "Number of People (Ones)", "Health Insurance in New Jersey")
```

# Income
## Median Income in New Jersey by Census Tract

```{r}
income <- alco_func("income")
income
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", income)

#map_func(income, "income", "income")

income_map <- income %>%
    leaflet(width = "100%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(
      label = ~ str_extract(NAME.y, "^([^,]*)"),
      stroke = FALSE,
      smoothFactor = 0,
      fillOpacity = 0.7,
      color = ~ pal(estimate)
    ) %>%
    addLegend("bottomright",
      pal = pal,
      values = ~estimate,
      title = "Income (Dollars)",
      opacity = 1
    ) %>%
# Adding the museums
    addControl("Median Income in New Jersey", position = "topright") %>% 
    addCircleMarkers(
      lng= m$Longitude, lat= m$Latitude, radius = 1,
      label= m$Museum.Name,
      labelOptions = labelOptions(direction = 'bottom',
                                offset=c(0,15)))

income_map

```

# Car Ownership
## Number of Cars Owned by Census Tract

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", car)

map_func(car, "Number of Cars (Ones)", "Number of Cars Owned in New Jersey")
```

# People with Self-Employment Income
## Number of People Who Reported to Having Self-Income

```{r}
self_income <- alco_func("self_income")
self_income
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", self_income)

map_func(self_income, "Number of People (Ones)", "Number of People Who Reported to Having Self-Income")
```

# Moved from Different State (House)
## Number of People who Moved from a Different State and Now Live in a House

```{r}
diff_stateHouse <- alco_func("diff_stateHouse")
diff_stateHouse
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", diff_stateHouse)

map_func(diff_stateHouse, "Number of People (Ones)", "Number of People who Moved from a Different State and Now Live in a House")
```

# Moved from Different State (Rent)
## Number of People who Moved from a Different State and Now Live in a Rental Unit

```{r}
diff_stateRent <- alco_func("diff_stateRent")
diff_stateRent
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", diff_stateRent)

map_func(diff_stateRent, "Number of People (Ones)", "Number of People who Moved from a Different State and Now Live in a Rental Unit")
```

# Moved from Different County (House)
## Number of People who Moved from a Different County and Now Live in a House

```{r}
diff_countyHouse <- alco_func("diff_countyHouse")
diff_countyHouse
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", diff_countyHouse)

map_func(diff_countyHouse, "Number of People (Ones)", "Number of People who Moved from a Different County and Now Live in a House")
```

# Moved from Different County (Rent)
## Number of People who Moved from a Different State and Now Live in a Rental Unit

```{r}
diff_countyRent <- alco_func("diff_countyRent")
diff_countyRent
```

```{r}
# Creating pallette to use with leaflet
pal <- pal_func("viridis", diff_countyRent)

map_func(diff_countyRent, "Number of People (Ones)", "Number of People who Moved from a Different County and Now Live in a Rental Unit")
```











